Linear regression for approximating real and synthetic data

### 2022-10-11 doc/paper.tex
grammar change
More paper

First, we will go more into depth about the methods and the theory behind them, along with a brief description of our implementation. We will further continue to the results, followed up by a critical discussion of the results. Finally, we will give a conclusion on the optimal model selection for the different datasets.

@@

\begin{table*}
\caption{This table shows the command to execute to reproduce every figure in the report. (More info about the scripts and their parameters can be found in the README)}
\begin{center}
\label{allparamstable}
\begin{tabular}{c | l l l}
Figure & Shell command (leading \texttt{python3} omitted) \\
\hline
\ref{frankenonoise} & \texttt{task\_b.py --noise 0 -n 25}\\
\ref{frankebestlambdamse} & \texttt{task\_b.py --noise 0 -n 25} \footnotesize{(\it Model has been changed to ridge with lambda=$1.43 \cdot 10^{-7}$)}\\
\ref{frankebestlambdabetas} & \texttt{task\_b.py --noise 0 -n 25} \footnotesize{(\it Model has been changed to ridge with lambda=$1.43 \cdot 10^{-7}$)}\\
\ref{realunscaled} & \texttt{task\_b.py --file ../data/small\_SRTM\_data\_Norway\_1.tif -n 19 --noscale}\\
\ref{realunscaledmse} & \texttt{task\_b.py --file ../data/small\_SRTM\_data\_Norway\_1.tif -n 19 --noscale}\\
\ref{frankenonoisemse} & \texttt{task\_c.py --noise 0 -n 24}\\
\ref{frankenoisemse} & \texttt{task\_c.py -n 24}\\
\ref{frankiebiasvariance} & \texttt{task\_c.py -n 24 --step 0.1}\\
\ref{frankiedifflambdas} & \texttt{task\_e\_biasvariance.py -n 24 --step 0.1}\\
\ref{frankedifflambdaslasso} & \texttt{task\_f\_biasvariance.py -n 9}\\
\ref{real1ridgedifflambdas} & \texttt{task\_e\_biasvariance.py --file ../data/small\_SRTM\_data\_Norway\_1.tif -n 24}\\
\ref{real1msecomparison} & \texttt{task\_f\_biasvariance.py --file ../data/small\_SRTM\_data\_Norway\_1.tif -n 9}\\
\ref{frankeridgebetas} & \texttt{task\_e\_betas.py -n 24}\\
\ref{frankenoisybeta} & \texttt{task\_c.py -n 24}\\
\ref{frankienoisecomparison} & \texttt{noise\_plot.py}\\
\ref{frankiehigherdatapoints} & \texttt{task\_c.py --noise 0 -n 30 --step 0.01}\\
\ref{real1surfacecomp} & \texttt{task\_b.py --file ../data/small\_SRTM\_data\_Norway\_1.tif -n 19}\\
\ref{real1mselessdata} & \texttt{task\_c.py --file ../data/tiny\_SRTM\_data\_Norway\_1.tif -n 19}\\
\ref{real1msetraintest} & \texttt{task\_c.py --file ../data/small\_SRTM\_data\_Norway\_1.tif -n 19}\\
\ref{realbiasvarianceOLS} & \texttt{task\_c.py --file ../data/small\_SRTM\_data\_Norway\_1.tif -n 19}\\
\ref{realOLSmse40} & \texttt{task\_b.py --file ../data/small\_SRTM\_data\_Norway\_1.tif -n 40}\\
\ref{realOLSbetaprog40} & \texttt{task\_b.py --file ../data/small\_SRTM\_data\_Norway\_1.tif -n 40}\\
\ref{frankemsebyresamplingmethod} & \texttt{task\_d.py -n 15 --step 0.02}\\
\ref{real1msecomparison} & \texttt{task\_f\_msecomparison.py --file ../data/small\_SRTM\_data\_Norway\_1.tif -n 9}\\
\hline
\end{tabular}
\end{center}
\end{table*}

@@

\begin{figure*}
\centerline{\includegraphics[width=3.25in]{figure/frankedifflambdaslasso.png}}
\caption{Bias, variance and test MSE plotted over polynomial degree for our Lasso prediction on the Franke function with an added stochastic noise $\epsilon \sim N(0,0.05)$, using lambdas of increasing size. Here we have reduced the number of datapoints to only 100 to force overfitting earlier.}
\label{frankedifflambdaslasso}
\end{figure*}

>>>>

First, we will go more into depth about the methods and the theory behind them, along with a brief description of our implementation. We will further continue to the results, alongside a critical discussion of the results. Finally, we will give a conclusion on the optimal model selection for the different datasets.

@@

\begin{table*}
\caption{This table shows the command to execute to reproduce every figure in the report. (More info about the scripts and their parameters can be found in the README)}
\begin{center}
\label{allparamstable}
\begin{tabular}{c | l l l}
Figure & Shell command (leading \texttt{python3} omitted) \\
\hline
\ref{frankenonoise} & \texttt{task\_b.py --noise 0 -n 25}\\
\ref{frankebestlambdamse} & \texttt{task\_b.py --noise 0 -n 25} \footnotesize{(\it Model has been changed to ridge with lambda=$1.43 \cdot 10^{-7}$)}\\
\ref{frankebestlambdabetas} & \texttt{task\_b.py --noise 0 -n 25} \footnotesize{(\it Model has been changed to ridge with lambda=$1.43 \cdot 10^{-7}$)}\\
\ref{realunscaled} & \texttt{task\_b.py --file ../data/small\_SRTM\_data\_Norway\_1.tif -n 19 --noscale}\\
\ref{realunscaledmse} & \texttt{task\_b.py --file ../data/small\_SRTM\_data\_Norway\_1.tif -n 19 --noscale}\\
\ref{frankenonoisemse} & \texttt{task\_c.py --noise 0 -n 24}\\
\ref{frankenoisemse} & \texttt{task\_c.py -n 24}\\
\ref{frankiebiasvariance} & \texttt{task\_c.py -n 24 --step 0.1}\\
\ref{frankiedifflambdas} & \texttt{task\_e\_biasvariance.py -n 24 --step 0.1}\\
\ref{frankedifflambdaslasso} & \texttt{task\_f\_biasvariance.py -n 9 --step 0.15}\\
\ref{real1ridgedifflambdas} & \texttt{task\_e\_biasvariance.py --file ../data/small\_SRTM\_data\_Norway\_1.tif -n 24}\\
\ref{frankeridgebetas} & \texttt{task\_e\_betas.py -n 24}\\
\ref{frankenoisybeta} & \texttt{task\_c.py -n 24}\\
\ref{frankienoisecomparison} & \texttt{noise\_plot.py}\\
\ref{frankiehigherdatapoints} & \texttt{task\_c.py --noise 0 -n 30 --step 0.01}\\
\ref{real1surfacecomp} & \texttt{task\_b.py --file ../data/small\_SRTM\_data\_Norway\_1.tif -n 19}\\
\ref{real1mselessdata} & \texttt{task\_c.py --file ../data/tiny\_SRTM\_data\_Norway\_1.tif -n 19}\\
\ref{real1msetraintest} & \texttt{task\_c.py --file ../data/small\_SRTM\_data\_Norway\_1.tif -n 19}\\
\ref{realbiasvarianceOLS} & \texttt{task\_c.py --file ../data/small\_SRTM\_data\_Norway\_1.tif -n 19}\\
\ref{realOLSmse40} & \texttt{task\_b.py --file ../data/small\_SRTM\_data\_Norway\_1.tif -n 40}\\
\ref{realOLSbetaprog40} & \texttt{task\_b.py --file ../data/small\_SRTM\_data\_Norway\_1.tif -n 40}\\
\ref{frankemsebyresamplingmethod} & \texttt{task\_d.py -n 15 --step 0.02}\\
\ref{real1msecomparison} & \texttt{task\_f\_msecomparison.py --file ../data/small\_SRTM\_data\_Norway\_1.tif -n 9}\\
\hline
\end{tabular}
\end{center}
\end{table*}

@@

\begin{figure*}
\centerline{\includegraphics[width=3.25in]{figure/frankedifflambdaslasso.png}}
\caption{Bias, variance and test MSE plotted over polynomial degree for our Lasso prediction on the Franke function with an added stochastic noise $\epsilon \sim N(0,0.05)$, using lambdas of increasing size. Here we have reduced the number of datapoints to less than 100 to force overfitting earlier.}
\label{frankedifflambdaslasso}
\end{figure*}
